DSSynth: An Automated Digital Controller Synthesis Tool for Physical Plants

### 2017-06-30 ase2017/paper.tex
intro editing

There are various mathematical representations for control 
systems,  e.g.,  transfer functions and state-space equations (difference or differential equations). 
Here, 
systems with a single input and a single output (SISO) are considered and 
represented by transfer functions or state-space LTI models. LTI models 
are used in several engineering applications to support non-trivial tasks when 
applied to embedded \& cyber-physical systems (e.g., robot manipulator, smart grid, 
power plants, distributed robotics, and automatic pilot avionics). 
The following expression presents the general form 
of a discrete plant or a digital controller based on the transfer function representation:
%
\begin{equation}
\small
\label{eq:transferfunction}
H(z)=\frac{B(z)}{A(z)}=\frac{b_{0}+b_{1}z^{-1}+...+b_{M}z^{-M}}{1+a_{1}z^{-1}+...+a_{N}z^{-N}},
\end{equation}
%
\noindent where $z^{-1}$ is called the backward-shift operator; $A(z)$ and $B(z)$ are 
the denominator and numerator polynomials; and $N$ and $M$
represent the denominator and numerator polynomials order, respectively.
%
In a state-space form, 
the behavior of a system is represented via a state evolution equation $x(n+1)$ and an instantaneous 
output equation $y(n)$, as follows:
%
\begin{equation}
\begin{split}
x(n+1) &= A x(n) + B u(n)
\\
y(n) &= C x(n) + D u(n), 
\end{split}\label{eq:ss-example}
\end{equation}

@@

Recently, a new methodology to synthesize digital control systems has been proposed, 
named DSSynth (Digital-System Synthesizer)~\cite{abate2017, abatecav2017}, 
which is based on the Counter-Example Guided Inductive Synthesis 
(CEGIS) approach~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06}. Here, CEGIS is used
as a program synthesis engine that is able to generate sound digital controllers for highly non-trivial 
control system specifications with a very high degree of automation. Program synthesis engines 
use a specification as the starting point, and subsequently produce a sequence of candidate 
programs from a given template. The candidate programs are iteratively refined to eventually 
satisfy the specification. Modern synthesis engines such as the one used here combine automated testing, genetic algorithms 
and SMT-based automated reasoning~\cite{DBLP:journals/corr/AlurFSS16a, DBLP:conf/lpar/DavidKL15}. 
DSSynth synthesizes stable digital controllers using the CEGIS-based approach,
for a given physical plant represented by either transfer functions or state-space equations~\cite{abate2017,abatecav2017}.

>>>>

There are various mathematical representations for control 
systems,  e.g.,  transfer functions and state-space equations (difference or differential equations). 
Here, 
systems with a single input and a single output (SISO) are considered and 
represented by transfer functions or state-space LTI models. LTI models 
are used in several engineering applications to support non-trivial tasks when 
applied to embedded \& cyber-physical systems (e.g., robot manipulator, smart grid, 
power plants, distributed robotics, and automatic pilot avionics). 
The following expression presents the general form 
of a discrete plant or a digital controller based on the transfer function representation:
%
\begin{equation}
\small
\label{eq:transferfunction}
H(z)=\frac{B(z)}{A(z)}=\frac{b_{0}+b_{1}z^{-1}+...+b_{M}z^{-M}}{a_{0}+a_{1}z^{-1}+...+a_{N}z^{-N}},
\end{equation}
%
\noindent where $z^{-1}$ is called the backward-shift operator; $A(z)$ and $B(z)$ are 
the denominator and numerator polynomials; and $N$ and $M$
represent the denominator and numerator polynomials order, respectively.
%
In a state-space form, 
the behavior of a system is represented via a state evolution equation $x(n+1)$ and an instantaneous 
output equation $y(n)$, as follows:
%
\begin{equation}
\begin{split}
x(n+1) &= A x(n) + B u(n)
\\
y(n) &= C x(n) + D u(n), 
\end{split}\label{eq:ss-example}
\end{equation}

@@

Recently, a new methodology to synthesize digital control systems has been proposed, 
named DSSynth (Digital-System Synthesizer)~\cite{abate2017, abatecav2017}, 
which is based on the Counter-Example Guided Inductive Synthesis 
(CEGIS) approach~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06}. Here, CEGIS is used
as a program synthesis engine that is able to generate sound digital controllers for highly non-trivial 
control system specifications with a very high degree of automation. The program synthesis engine 
uses a specification as starting point, and subsequently produces a sequence of candidate 
programs from a given template. The candidate programs are iteratively refined to eventually 
satisfy the specification. Modern synthesis engines such as the one used here combine automated testing, genetic algorithms 
and SMT-based automated reasoning~\cite{DBLP:journals/corr/AlurFSS16a, DBLP:conf/lpar/DavidKL15}. 
Using the CEGIS-based approach, DSSynth synthesizes stable digital controllers
for a given physical plant represented by either transfer functions or state-space equations~\cite{abate2017,abatecav2017}.
